Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis

### 2019-09-18 zhf_manuscript/zhf_manuscript.Rmd
prisma right size
dataframe ma output

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis"
titlerunning: Short form of title (if too long for head)
authorrunning: Conway,
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

@@

- name: Âuthóř 2
  address: Department of ZZZ, University of WWW
  email: djf@wef

@@

  ```{r echo=FALSE, include=FALSE}
library(redcapAPI)
library(tidyverse)
library(kableExtra)
library(purrr)
library(ggplot2)
library(dplyr)
library(qwraps2)
library(rticles)
```
# Introduction

@@

Zero-heat-flux (ZHF) thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature. Originally developed in the 1970s, ZHF technology was recently implemented in the 3M SpotOn (3M, St Paul, MN), a single-use, disposable sensor $(ref)$. In practice, the ZHF sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and initially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues$(ref)$. Equipped with a thermal insulator, the ZHF sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature $(ref)$.

The agreement between ZHF and established core temperature devices has been investigated in several studies conducted within the clinical setting, each with varied results. Appraisal of these studies and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which ZHF may be used.

We aimed to determine if ZHF has clinically acceptable accuracy and precision relative to established core temperature measurement devices. Accuracy is defined as the average difference between temperature measurements from the ZHF and comparator device and precisions as the variance (typically reported as the SD) in the differences.

@@

A systematic review was conducted in accordance with a predetermined protocol (PROSPERO trial registration number: ################).

@@

Published studies were found by searching Medline and EMBASE from January 2000 to July 2019, 
>as well as the reference lists of articles identified to be relevant to the review.  This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies [@preston2015improving]. Unpublished and ongoing studies were located by searching the International Clinical Trials Platform.

Published conference abstracts were included if there was enough information reported to appraise the quality of the study. There were no language restrictions applied during the search. 
>The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should].

The search strategies used for each data base can be located in [file 1]().

The selection of studies was undertaken by two independent reviewers. Studies were included if reported measures from a ZHF and comparator device coincided. Studies involving a case control design were excluded due to potential for overestimation of the intervention performance. Studies were excluded if conducted on non-human subjects or outside of a clinical healthcare setting. Studies were excluded if conducted earlier than the year 2000 as prior studies evaluated outdated technology that is no longer relevant to current clinical practice.

@@

Information was extracted regarding study characteristics (author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and ZHF characteristics (placement of sensor, timing and methods of measurements). The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature measurement between the ZHF sensor and comparator device. 
>Information was extracted about how repeated measurements were handled: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].

Using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2), each reviewer independently assessed the risk of bias for the included studies [@whiting2011quadas]. Using guiding questions, reviewers rated the risk of bias for patient selection, conduct of the ZHF measurements, conduct of the comparator device measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear”. We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry [@glasziou2001systematic]. 
>Statistical analyses to detect reporting bias were not conducted due to lack of validated methods [@begg2005systematic]. Although some meta-analyses of method comparison studies have used tests for detecting funnel plot asymmetry [@niven2015accuracy], simulations have revealed that such tests will result in publication bias being incorrectly identified too often [@deeks2005performance].

@@

The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the ZHF and established comparator devices.
>The framework for meta-analysis of Bland-Altman method comparison studies based on limits of agreement (LoA) approach was used [@tipton2017framework].

This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled LoAs in the population (not just in the samples studied). The ‘population LoA’ is more broad than the LoA commonly reported in the meta-analyses of Bland-Altman studies [@tipton2017framework]. In these instances,
>the pooled LoAs are calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.

Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated SEs estimated using robust variance estimation (RVE). RVE was used alternatively to model-based SEs as several studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small]. We used the 
>method-of-moments estimator from ref 16 for the $\tau2$ parameter.

In accordance with ref 12, (1) measures of uncertainty were included 
>when interpreting the LoA estimates by calculating the outer $95\%$ CIs for pooled LoA;

and (2) repeated measurements were adjusted if improperly adjusted for in 
>individual studies (by using weights proportional to the number of participants, not the total number of measurements).

The formulas for the above calculations from ref 12 can be found in [file 1](). The R statistical program was used to conduct all analyses [@team2017r]. All data and R code (provided in ref 12) used in the meta-analyses can be located [here](https://doi.org).

Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $comparator-ZHF$ measured in $^\circ C$. In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'. Other studies reported multiple sets of results, whereby analyses were conducted between ZHF and various comparator devices used on the same participant. These instances were also treated as a separate 'comparison' if the comparator devices were apart of separate meta-analyses groups. One study reported intraoperative, postoperative and overall results for the same participants. Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups. The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 $^\circ C$ $(ref - most of the studies site this range from Eshragi...)$.
>It was deemed that outer confidence bounds for 95\% LoA between ECT and ZHF (termed as ‘population limits of agreement’) outside of these bounds would

be clinically unacceptable. Sensitivity analysis for the primary meta-analysis was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses. As clinicians would be interested in the accuracy of ZHF relative to the thermometer devices they use, and within the clinical setting in which they use it we conducted subgroup analyses according to the comparator device used (eg, core, peripheral, nasopharangeal) and clinical setting (eg, intraoperative, intensuve care unit).

@@

Sixteen studies were eligible for inclusion in this systematic review (Figure 1).

```{r echo=FALSE, fig.height=4.5}
knitr::include_graphics("figure_one.png")
```

@@

Using these studies, we conducted 6 different meta-analyses. The first group compared ZHF to core (eg, arterial, bladder, esophageal, rectal) temperature measurements and included 22 (73%) comparisons from 14 (%) studies, and enrolled 607 participants with 179,821 paired measurements. The second group compared ZHF to core temperature measurements in low risk bias studies studies that scored a low risk of bias in all categories) and included 10 (%) comparisons from 5 (%) studies, and enrolled 273 participants with 104,294 paired measurements. The third group compared ZHF to core temperature measurements in ICU patients and included 7 (23%) comparisons from 5 (31%) studies, and enrolled 246 participants with 155,598 paired measurements. The fourth group compared ZHF to core temperature measurement in intraoperative patients and included 16 (53%) comparisons from  10 (63%) studies, and enrolled 464 participants with 24,223 paired measurements. The fifth group compared ZHF to nasopharyngeal temperature measurements and included 4 (13%) comparisons from  4 (25%) studies, and enrolled 297 participants with 109,819 paired measurements. The sixth group compared ZHF to sublingual temperature measurement and included 2 (7%) comparisons from  2 (13%) studies, and enrolled 107 participants with 22731 paired measurements. The studies included in this systematic review evaluated a ZHF temperature monitoring system manufactured by 3M. Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF device is now referred to as the Bair Hugger Temperature Monitoring System. All comparisons reported adherence to the ZHF device manufacturer instructions and placed the sensor on the forehead of the participants. High risk of bias was associated with patient selection for 13 (43%) comparisons from 9 (56%) studies, conduct of ZHF and comparator measurements in 10(33%) comparisons from 8 (50%) studies and 12 (40%) comparisons 9 (30%) studies, respectively (mostly due to ZHF measurements being taken with knowledge of the comparator measurements and vice versa) and participant flow for 13 (43%) studies. In 19 (50%) comparisons from 8 (50%) studies, the authors had declared a conflict of interest or receipt of funding or equipment from the manufacturer of the ZHF device under evaluation.

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis"
titlerunning: Accuracy of zero-heat-flux temperature monitoring
authorrunning: Conway
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

@@

@@

```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(kableExtra)
library(purrr)
library(ggplot2)
library(dplyr)
library(qwraps2)
```
# Introduction

@@

Zero-heat-flux thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature. Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M SpotOn (3M, St Paul, MN), a single-use, disposable sensor $(ref)$. In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and initially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues$(ref)$. Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature $(ref)$.

The agreement between zero-heat-flux thermometers and core as well as other peripheral thermometers has been investigated in several studies conducted within clinical settings. Appraisal of these studies and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which zero-heat-flux thermometers may be used. We aimed to determine if zero-heat-flux thermometers have clinically acceptable accuracy and precision relative to established core and peripheral temperature measurement devices. Accuracy is defined as the average difference between temperature measurements from the zero-heat-flux and comparator device and precision as the variance (standard deviation) in the differences.

@@

A systematic review was conducted in accordance with a predetermined protocol. The protocol was submitted to PROSPERO for registration but due to delays in processing we had started data extraction by the time it was reviewed. Therefore, the protocol did not meet the requirements for registration. A copy of the submitted protocol can be accessed [here](insert link). The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus a temperature measured from a core site, which we defined as arterial, esophaeal, bladder and rectal sites. Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.

## Inclusion criteria

Observational studies that reported temperature measurements from a zero-heat-flux thermometer and comparator thermometer were included. Studies involving a case control design were excluded due to potential for overestimation of the intervention performance. Studies were excluded if conducted on non-human subjects or outside of a clinical healthcare setting. No publication date restrictions were applied.Published conference abstracts were included if there was enough information reported to appraise the quality of the study. There were no language restrictions applied during the search.

@@

Published studies were found by searching Medline and EMBASE from January 2000 to July 2019. The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should]. This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers. The search strategies used for each data base can be located in [file 1](). Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).

@@

Information was extracted regarding study characteristics (author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and temperature measurement characteristics (placement of sensor, timing and methods of measurements). The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature measurement between the zero-heat-flux and comparator thermometers. 
We also extracted information about how repeated measurements were handled. In particular we assessed whether studies: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].

Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2) [@whiting2011quadas]. Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias. We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry [@glasziou2001systematic]. Statistical approaches for detection of reporting bias were not conducted due to lack of validated methods [@begg2005systematic]. ASimulations have revealed that tests for detecting funnel plot asymmetry will result in publication bias being incorrectly identified too often [@deeks2005performance].

@@

The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the ZHF and established comparator thermometers. A framework for meta-analysis of Bland-Altman method comparison studies developed by @tipton2017framework based on limits of agreement approach was used. This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled LoAs in the population (not just in the samples studied). The ‘population LoA’ is more broad than the LoA commonly reported in the meta-analyses of Bland-Altman studies [@tipton2017framework]. Pooled limits of agreement were calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.

Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated standard errors estimated using robust variance estimation. Robust variance estimation was used alternatively to model-based standard errors as some studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small]. We used the method-of-moments estimator from @dersimonian1986meta for the $\tau2$ parameter.

Measures of uncertainty were included in our meta-analyses by calculating the outer $95\%$ confidence intervals for pooled limits of agreement. We also accounted for repeated measurements if they were not properly adjusted for in individual studies. This was achieved by using weights proportional to the number of participants, not the total number of measurements.  The R statistical program was used to conduct all analyses [@team2017r]. All data and R code used in the meta-analyses can be located [here]().

Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $comparator thermometer-ZHF thermometer$ measured in $^\circ C$. In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'. Other studies reported multiple sets of results, whereby analyses were conducted between ZHF and various comparator devices used on the same participant. These instances were also treated as a separate 'comparison' if the comparator devices were apart of separate meta-analyses groups. One study reported intraoperative, postoperative and overall results for the same participants. Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups.

The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 $^\circ C$ $(ref - most of the studies site this range from Eshragi...)$. It was deemed that outer confidence bounds for 95% LoA between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds wouldbe clinically unacceptable.

A sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses. As clinicians would be interested in the accuracy of ZHF relative to the thermometer devices they use, and within the clinical setting in which they use it, we conducted subgroup analyses according to the comparator device used (either core, sublingual or nasopharangeal) and clinical setting (either intraoperative or intensive care unit).

@@

Fifteen studies were included in this systematic review (Figure 1). Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.

```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE}
img <- magick::image_read("figure_one.png")
img %>% magick::image_scale("350")
```

```{r meta-function, echo=FALSE}
meta <-  function(Te,V_T){
m <- length(Te)
wt_FE=1/V_T
T_FE <- sum(Te*wt_FE)/sum(wt_FE)
Q <- sum(wt_FE*(Te - T_FE)^2)
S1 <- sum(wt_FE)
S2 <- sum(wt_FE^2)
o2 <- (Q - (m - 1))/(S1 - S2/S1)
wt_RE <- 1/(V_T + o2)
T_RE <- sum(Te*wt_RE)/sum(wt_RE)
V_T_RE_mod <- 1/sum(wt_RE)
V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
}
loa_maker <- function(bias,V_bias,logs2,V_logs2) {
bias_row=meta(bias, V_bias)
logs2_row=meta(logs2, V_logs2)
bias_mean <- bias_row[2]
sd2_est <- exp(logs2_row[2])
tau_est <- bias_row[3]
LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
m <- bias_row[1]
tcrit <- qt(1-.05/2,m-1)
B1 <- sd2_est^2/(sd2_est + tau_est)
B2 <- tau_est^2/(sd2_est + tau_est)
wt <- 1/V_bias
S1 <- sum(wt)
S2 <- sum(wt^2)
S3 <- sum(wt^3)
A0 <- 2*(m-1)/(S1-S2/S1)^2
A1 <- 4/(S1 - S2/S1)
A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
V_logT2 <- A0/tau_est^2 + A1/tau_est + A2
V_logT2 <- 2/sum((V_bias + tau_est)^(-2))
V_LOA_mod <- bias_row[4] + B1*logs2_row[4] + B2*V_logT2
V_LOA_rve <- bias_row[5] + B1*logs2_row[5] + B2*V_logT2
CI_L_mod <- LOA_L - tcrit*sqrt(V_LOA_mod)
CI_U_mod <- LOA_U + tcrit*sqrt(V_LOA_mod)
CI_L_rve <- LOA_L - tcrit*sqrt(V_LOA_rve)
CI_U_rve <- LOA_U + tcrit*sqrt(V_LOA_rve)
data.frame(m, bias_mean,sqrt(sd2_est), tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)
}
```

```{r load-data, include=FALSE}
library(tidyverse)
data <- readxl::read_xlsx(here::here("data","zhf_extracted.xlsx"))
```

```{r meta-analysis-prep, include=FALSE}
data <- data %>%

  mutate(c = N/n)

#variance

data <-  if (data$corrected == "Yes"){

  mutate(data, s2 = ((upper - bias)/1.96)^2)

  } else {

    mutate(data, s2 = ((upper - bias)/1.96)^2)*((N-1)/(N-c))

    }

data <- data %>% 
  mutate(V_bias = s2/n)

data <- data %>% 
  mutate(logs2 = log(s2)+1/(n-1))

data <- data %>% 
  mutate(V_logs2 = 2/(n-1))
```

```{r subgroups, include=FALSE}
# meta-analyses categories

data_NPA <- data %>% 
  filter(comparison == "NPA")

data_SL <- data %>% 
  filter(comparison == "Sublingual")

data_core <- data %>% #eshragi overall
  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")

data_core_op <- data%>% #eshragi intraop
    filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter (clinical_setting=="Intraoperative")

data_core_icu <- data %>% #eshragi postop
      filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")

# ROB

data_core_lowrisk <- data_core %>% #eshragi overall
  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")

# conflict of interests

data_conflict <- data_core %>% 
  filter(`Funding/equipment/conflict with ZHF company` == "Yes")

```

```{r format-result-function, include=FALSE}
format_results <- function(group){
out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
out <- round(out, digits=1)
out <- out %>% 
  mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
  mutate(Measurements = sum(group$N, na.rm = T)) %>% 
  mutate(Studies = length(unique(group$Study))) %>% 
  select(Studies, m, Participants, Measurements, bias_mean, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
  rename("Comparisons" = m, "Mean bias" = bias_mean, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve)
out
}
```

```{r primary, include=FALSE}
primary <- format_results(data_core)
```

```{r sensitivity-low-risk, include=FALSE}
low_risk <- format_results(data_core_lowrisk)
```

```{r NPA, include=FALSE}
NPA  <- format_results(data_NPA)
```

```{r SL, include=FALSE}
SL  <- format_results(data_SL)
```

```{r OT, include=FALSE}
OT  <- format_results(data_core_op)
```

```{r ICU, include=FALSE}
ICU  <- format_results(data_core_icu)
```

```{r conflict, include=FALSE}
conflict  <- format_results(data_conflict)
```

@@

The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies. In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis). The sensitivity analysis for the primary comparison with only studies that were judged as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r format(low_risk$Measurements, scientific=F)` paired measurements (two studies did not report the total number of measurements included in their analysis). The third group compared zero-heat-flux to core temperature measurements in ICU patients and included 7 (23%) comparisons from 5 (31%) studies, and enrolled 246 participants with 155,598 paired measurements. The fourth group compared ZHF to core temperature measurement in intraoperative patients and included 16 (53%) comparisons from  10 (63%) studies, and enrolled 464 participants with 24,223 paired measurements. The fifth group compared ZHF to nasopharyngeal temperature measurements and included 4 (13%) comparisons from  4 (25%) studies, and enrolled 297 participants with 109,819 paired measurements. The sixth group compared ZHF to sublingual temperature measurement and included 2 (7%) comparisons from  2 (13%) studies, and enrolled 107 participants with 22731 paired measurements. The studies included in this systematic review evaluated a ZHF temperature monitoring system manufactured by 3M. Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF device is now referred to as the Bair Hugger Temperature Monitoring System. All comparisons reported adherence to the ZHF device manufacturer instructions and placed the sensor on the forehead of the participants. High risk of bias was associated with patient selection for 13 (43%) comparisons from 9 (56%) studies, conduct of ZHF and comparator measurements in 10(33%) comparisons from 8 (50%) studies and 12 (40%) comparisons 9 (30%) studies, respectively (mostly due to ZHF measurements being taken with knowledge of the comparator measurements and vice versa) and participant flow for 13 (43%) studies. In 19 (50%) comparisons from 8 (50%) studies, the authors had declared a conflict of interest or receipt of funding or equipment from the manufacturer of the ZHF device under evaluation.
